PANNEURO_analysis

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd

```{r age_category per Sample prop per Sample}
age_category_per_Sample_prop_Sample <- dat.raw %>%
  group_by(Sample) %>%
  count(age_category, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

@@

## Cross tables
```{r age_category per Sample prop cross table}
age_category_per_Sample_prop_Sample_cross_table <- dat.raw %>%
  group_by(Sample) %>%
  count(age_category, Sample) %>%
  mutate(Prop = round(n/sum(n), 2)) %>%
  pivot_wider(names_from = Sample, values_from = c(n, Prop))

@@

```{r sex according to probable Covid}
sex_category_per_Covid_prop_total <- dat.raw %>%
  filter(!is.na(Sex)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  count(Sex, covid_probable_case_incl_screening) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(sex_category_per_Covid_prop_total)
sex_category_per_Covid_prop_total
```

## Smoking not available

## BMI not available

@@

```{r}
key_worker_category_per_Covid_prop_total <- dat.raw %>%
  filter(!is.na(key_worker)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  count(key_worker, covid_probable_case_incl_screening) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(key_worker_category_per_Covid_prop_total)
key_worker_category_per_Covid_prop_total
```

>>>>

```{r age_category per Sample prop per Sample}
age_category_per_Sample_prop_Sample <- dat %>%
  group_by(Sample) %>%
  count(age_category, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

@@

## Cross tables
```{r age_category per Sample prop cross table}
age_category_per_Sample_prop_Sample_cross_table <- dat %>%
  group_by(Sample) %>%
  count(age_category, Sample) %>%
  mutate(Prop = round(n/sum(n), 2)) %>%
  pivot_wider(names_from = Sample, values_from = c(n, Prop))

@@

## Smoking

## BMI

@@
